Clean - An Abstract Imperative Programming Language and its Theory

### 2019-09-10 C11-BackEnds/Clean/document/root.tex
document

\title{Clean - An Abstract Imperative Programming Language and its Theory}
\author{Frederic Tuong and Burkhart Wolff \\ (with Contributions of Chantal Keller)}
\maketitle

\begin{abstract}
Clean (pronounced as: ``C lean'') is based on a simple, abstract execution model for an 
imperative target language. "Abstract" is understood as contrast to "Concrete Semantics";
alternatively, the term "shallow-style embedding" could be used.

Clean is based on a ``no-frills'' state-exception monad  with the 
usual definitions of \verb+bind+ and \verb+unit+ for the compositional glue of
state-based computations. Clean offers conditionals and loops supporting C-like 
control-flow operators such as \verb+break+ and \verb+return+.
The memory model is fully \HOL -typed and based on a construction nesting
subsequently extensible records. Note that the current version only supports
monomorphic states and parameters of (directly recursive) functions.

The design is striving for extreme simplicity. It is geared towards symbolic execution and
proven correct verification tools. The underlying libraries of this package, however,
deliberately restricts itself to the most elementary infrastructure for these tasks. 
The package is intended to serve as demonstrator semantic backend for Isabelle/C \cite{TuongWolff19},
serving as basis for the test-generation technique described in \cite{DBLP:conf/tap/Keller18} .
\end{abstract}

>>>>

\title{Clean - An Abstract Imperative Programming Language and its Theory}
\author{%
  \href{https://www.lri.fr/~ftuong/}{Fr\'ed\'eric Tuong}
  \and
  \href{https://www.lri.fr/~wolff/}{Burkhart Wolff} \\
  \and
  (with Contributions of \href{https://www.lri.fr/~keller/}{Chantal Keller})}
\publishers{%
  \mbox{LRI, Univ. Paris-Sud, CNRS, Universit\'e Paris-Saclay} \\
  b\^at. 650 Ada Lovelace, 91405 Orsay, France \texorpdfstring{\\}{}
}

\maketitle

\begin{abstract}
Clean (pronounced as: ``Céline'' [selin]) is based on a simple, abstract execution model for an
imperative target language. ``Abstract'' is understood as contrast to ``Concrete Semantics'';
alternatively, the term ``shallow-style embedding'' could be used.

Clean is based on a ``no-frills'' state-exception monad with the usual definitions of \isa{bind} and
\isa{unit} for the compositional glue of state-based computations. Clean offers conditionals and
loops supporting C-like control-flow operators such as \isa{break} and \isa{return}. The memory
model is fully \HOL{}-typed and based on a construction nesting subsequently extensible
records. Note that the current version only supports monomorphic states and parameters of (directly
recursive) functions.

The design is striving for extreme simplicity. It is geared towards symbolic execution and proven
correct verification tools. The underlying libraries of this package, however, deliberately
restricts itself to the most elementary infrastructure for these tasks. The package is intended to
serve as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, serving as basis for the
test-generation technique described in~\cite{DBLP:conf/tap/Keller18}.
\end{abstract}
